\documentclass{article}
\usepackage{amssymb,amsmath,indentfirst}
\usepackage{todonotes}
\usepackage{graphicx}
\newcommand{\entities}{{\cal E}}
\newcommand{\ent}{e}
\newcommand{\roles}{{\cal R}} 
\newcommand{\role}{r}
\newcommand{\Tv}{T}
\newcommand{\tv}{t}
\newcommand{\sent}{s}
\newcommand{\weight}{\mathbf{w}}
\newcommand{\rend}{\rho}
\newcommand{\Rend}{{\cal P}}
\newcommand{\trans}{q}
\newcommand{\obj}{f}
\newcommand{\commentout}[1]{}
\newcommand{\Enum}[1]{\{1 \ldots #1\}}
\newcommand{\EnumS}[2]{\{#1 \ldots #2\}}
\newcommand{\Set}[1]{\big\{ #1 \big\}}
\newcommand{\Bin}[1]{\{0,1\}^{#1}}
\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\argmin}{arg\,min}
\newcommand{\rot}[1]{\rotatebox{90}{#1}} 
\newcommand{\fmap}{\boldsymbol{\phi}}
\newcommand{\edgeTot}{\boldsymbol{\psi}}

\begin{document}


\section{Introduction}


Automatic coherence assessment has typically examined the effect of local discourse features on coherence. These features are typically sentence-to-sentence transitions of entities, discourse relations, or other sentential information. 
Additionally, this task is often framed as selecting the most coherent ordering of a set of sentences in a document, where the original ordering as written by a human is assumed to be the most coherent ordering.


\section{Related Work}


Local coherence has been strongly influenced by Centering Theory \cite{grosz1995centering}, which places constraints on discourse entities and their transitions between text units.
Moreover, it establishes the importance of entity salience, and syntactic role for local coherence. 
While not directly implementing these constraints, \cite{barzilay2005modeling} uses discourse entities in formulating an \textit{entity grid} model for learning sentence-to-sentence transition features that contribute to document coherence. 
Additionally, \cite{barzilay2005modeling} establish the sentence ordering task such that training data can be generated in an unsupervised fashion.   
The entity grid model, and its variants, have remained popular in the discourse coherence literature, as various authors have tried to augment it with global features \cite{elsner2007unified}, more direct coreference features \cite{elsner2008coreference}, discourse connectives \cite{lin2011automatically}, and syntax patterns \cite{louis2012coherence}.  


Few authors have dealt directly with the issues of intractability. 
\cite{althaus2004computing} prove the sentence ordering task is an NP complete problem by showing its reducibility to a traveling salesperson problem. 
\cite{soricut2006discourse} uses an IDL (Interleave-Disjunction-Lock) graph formalism to compactly represent the search space of sentence-to-sentence transitions in the ordering problem, and experiment with A* and beam search algorithms for learning/decoding.                    
The IDL formalism allows for a complex scoring for sentence to sentence transitions, while using an admissible heuristic to prevent \textit{unfolding} unnecessary search states. 
Unfortunately, their implementation exhibits run times of over a minute for problems of only eleven sentences, indicating this approach may not scale for some applications.
\todo[inline]{Put sauper and barzilay 2009 in here for topic level discourse ordering and ILP solver implementation.}



\section{Entity Grid Model}

The {\em entity grid} model is a popular local coherence model where a document rendering is represented by a matrix or grid of discourse entities and their syntactic role, such as the \textit{subject}, \textit{object}, etc. 
Each entity in the document has a column and each sentence has a row in the grid. 
A role transition is simply a column subsequence of any length. For example, in Table ~\ref{tab:egrid} the entity \textit{winds} has a length 2 transition \{-,o\} in sentences 2--3. 


\begin{table}[h]
\begin{center}
    \begin{tabular}{ l | l  l  l  l  l  l  l  l  l  l  l  }
    & \rot{Karen}  & \rot{winds}  & \rot{Friday} & \rot{Wash., D.C.} & \rot{Monday} & \rot{Gulf of Mexico} & \rot{coast} & \rot{weekend} & \rot{authorities} & \rot{orders} & \rot{New Orleans} \\ \hline
    $\mathbf{1}$ & s & - & - & - & - & x & x & x & - & - & - \\ 
    $\mathbf{2}$ & s & - & x & - & - & - & x & - & s & o & x \\ 
    $\mathbf{3}$ & s & o & x & - & - & - & - & - & - & - & - \\ 
    $\mathbf{4}$ & s & - & - & x & x & - & - & - & - & - & - \\ 
    \end{tabular}
\end{center}
\caption[Entity grid representation]{An example entity grid representation.}
\label{tab:egrid}
\end{table}

Let a document $d$ be an unordered set of $n$ sentences. 
We define the set $\entities = \{e_1,e_2,\ldots,e_{|\entities|}\}$ to be the set of $|\entities|$ entities that occur in $d$ and the set $\roles$ to be a finite set of syntactic roles. 
We also define the set of document renderings $\Rend = \{\rend_1,\rend_2,\ldots, \rend_{n!} \}$ to be the set of ordered permutations of these sentences. 
A document rendering $\rend_i = \{\sent_{i,j} : 1 \le j \le n \}$ is an ordered sequence of sentences where a sentence is a vector $\sent_{i,j} = \{\role_{i,j,\ent_k} : 1\le k \le |\entities| \}$ of syntactic roles.


We formally define the entity grid model of a document rendering $\rend_i$ to be the sets $\entities$, $\roles$, and the set of transition vectors $\tv_{i,j}$  for all $j$, $2 \le j \le n$. 
A transition vector $\tv_{i,j} \in \{\roles\times\roles\}^{|\entities|}$ is a vector of entity role transitions from $\sent_{i,j-1}$ to $\sent_{i,j}$ where each element corresponds to a transition  $\trans \in \{\roles\times\roles\}$.
Define the function $\fmap: \Rend \rightarrow \mathbb{R}^{| \roles \times \roles | }$ with $\fmap(\rend_i) = \{ \phi_\trans(\rend_i) : \forall \trans \in {\roles \times \roles}  \}$ and

\begin{equation}
\phi_\trans(\rend_i) = \frac{ \displaystyle \sum_{j = 2}^n \sum_{k=1}^{|\entities|} I(\tv_{i,j,e_k}= \trans)  }{|\entities|(n-1)}. 
\end{equation}


Given a vector of weights $\mathbf{w} \in \mathbb{R}^{|\roles\times\roles|}$, we define our objective function $\obj : \mathbb{R}^{|\roles\times\roles|}  \rightarrow \mathbb{R}$ where $\obj(\fmap(\rend_i);\weight) = \weight\cdot\fmap(\rend_i)$. 
The sentence ordering task can further be defined as finding the rendering that maximizes this function, or

\begin{equation}
    \argmax_{i \in \EnumS{1}{n!}} \obj(\boldsymbol{\phi}(\rend_i) ; \weight ).
\end{equation}


Solving this problem for larger documents is intractable as the time complexity of computing the $\argmax$ is $ O(|\Rend||\roles|^2) = O(n!|\roles|^2)$; to compute each ranking, we must perform $|\roles|^2$ multiplications, and to find the maximum we must check $n!$ possible renderings.

\section{TSP Formulation}
We formulate this problem as a Traveling Salesperson Problem where each sentence $\sent$ is a vertex in a fully connected graph. 
Adding an edge $(\sent_i,\sent_j)$ to the solution path represents selecting $\sent_j$ as the next sentence in the document rendering.
In order to calculate edge weights, we define a function $\edgeTot : E \rightarrow \mathbb{Z}^{|\roles \times \roles|}  $ where $\edgeTot(s_i,s_j) = \{ \psi_\trans(s_i,s_j) : \trans \in {\roles \times \roles } \}$ and 
\begin{equation}
    \psi_\trans\left( s_i,s_j \right) = \displaystyle \sum_{k=1}^{|\entities|} I\left( \langle s_{i,\ent_k},s_{j,\ent_k} \rangle = \trans\right) . 
\end{equation}

Edge weights are determined by the function

\begin{equation}
    g(\edgeTot(\sent_i,\sent_j );\weight) = \weight\cdot \edgeTot(\sent_i, \sent_j) = \sum^{|\roles|^2}_{q=1} w_\trans \left( \sum_{k = 1}^{|\entities|} I(\langle \sent_{i,\ent_k},\sent_{j,\ent_k}\rangle = \trans) \right).
\end{equation}

where $\langle \sent_{i,\ent_k},\sent_{j,\ent_k} \rangle$ is a transition $q \in \{\roles \times \roles\}$ for entity $k$  obtained from ordered sequence of $\sent_i,\sent_j$.


Under this formulation, the optimal path is equivalent to the solution to the optimal rendering in the entity grid formulation. 
The total edge weights for the optimal path are the sum of $g(\edgeTot(\sent_i,\sent_j);\weight)$ for all $(\sent_i,\sent_j)$ in the path.
Without loss of generality, let the optimal path $\rend = \{ \sent_1,\sent_2,\ldots,\sent_n \}$.

\begin{equation*}
\begin{split}
\textrm{Optimal Path Edge Weight} &= \sum^{n}_{j=2} g(\edgeTot(\sent_{j-1},\sent_j );\weight) \\
& = \sum^n_{j=2} \sum^{|\roles|^2}_{\trans=1} w_\trans \left( \sum_{k = 1}^{|\entities|} I(\langle \sent_{j-1,\ent_k},\sent_{j,\ent_k}\rangle = \trans)  \right)\\
& = \sum^{|\roles|^2}_{\trans=1} w_\trans \left( \sum^n_{j=2}  \sum_{k = 1}^{|\entities|} I(\langle \sent_{j-1,\ent_k},\sent_{j,\ent_k}\rangle = \trans)  \right)\\
%& = \sum^\rend_{t} \sum^{|\roles|^2}_{i=1} w_i \Big( \sum_{j\in1,\ldots,|\entities|} I(\tv_{j}= r_i) \Big)\\
%& = \sum^{|\roles|^2}_{i=1} w_i \Big( \sum^\rend_{t} \sum_{j\in1,\ldots,|\entities|} I(\tv_{j}= r_i) \Big)\\
\end{split}
\end{equation*}

Equivalently the $\argmax$ of the Entity Model objective function is


\begin{equation*}
\begin{split}
    \argmax_{i \in \EnumS{1}{n!}} \obj(\fmap(\rend_i) ; \weight ) &= \argmax_{i \in \EnumS{1}{n!}} \sum^{|\roles|^2}_{\trans=1} w_\trans \left(  \frac{ \displaystyle \sum_{j = 2}^n \sum_{k=1}^{|\entities|} I(\tv_{i,j,e_k}= \trans)  }{|\entities|(n-1)} \right)\\    
    &= \argmax_{i \in \EnumS{1}{n!}} \sum^{|\roles|^2}_{\trans=1} w_\trans \left( \displaystyle \sum_{j = 2}^n \sum_{k=1}^{|\entities|} I(\tv_{i,j,e_k}= \trans)\right)\\    
    &= \argmax_{i \in \EnumS{1}{n!}} \sum^{|\roles|^2}_{\trans=1} w_\trans \left( \displaystyle \sum_{j = 2}^n \sum_{k=1}^{|\entities|}I(\langle\sent_{i,j-1,\ent_k},\sent_{i,j,\ent_k} \rangle   = \trans)\right)\\    
%\argmax_{\rend \in \Rend} \obj(\boldsymbol{\phi}_\rend ; \weight ) & =\operatorname{arg} \max_{\rend \in \Rend}\sum^{|\roles|^2}_{i=1} w_i \Big( \frac{\sum_{\tv}^\rend\sum_{j\in1,\ldots,|\entities|} I(\tv_{j}= r)  }{|\entities|(n-1)}   \Big)\\
%&  =\argmax_{\rend \in \Rend}\sum^{|\roles|^2}_{i=1} w_i \Big( \sum_{\tv}^\rend\sum_{j\in1,\ldots,|\entities|} I(\tv_{j}= r)     \Big)\\
\end{split}
\end{equation*} 

\todo{give an example. NetworkX}


\bibliographystyle{plain}
\bibliography{write-up}
\end{document}

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: t
%%% End: 
